### 2009-09-16 latex/paper1/contents.tex
paper

Development of large-scale software systems is a challenge. \cite{Northrop2006}

A key to success is the ability to decompose a system into weakly-coupled
modules, so each module can be developed by a distinct team. Failing to do so
results in duplicated code, non-parallelism, one's work impacting another's work
etc.

@@

POR ISSO SURGIRAM software modularization recovery algorithms, also known as
software clustering algorithms or software architecture recovery algorithms. In
its most common flavor, these algorithms analyze the dependencies between
implementation components, such as classes, and then group them into modules
such as there are few dependencies between classes in distinct modules.
\cite{Pollet2007}

@@

% TODO: diagram showing the evaluation of a clustering algorithm

@@

Of course the success of this approach depends on the realism of the synthetic
networks, ie, how well they resemble networks extracted from real software
systems. In this paper we study three models and show that all of them are, by
means of a careful parameter choosing, capable of producing realistic software
networks.

@@

\begin{itemize}
\item $p, q, r \in {0.0, 0.2, 0.4, 0.6, 0.8, 1.0}$, with $p + q + r = 1$ and $p
+ q > 0$;
\item $din, dout \in {0, 1, 2, 3, 4}$;
\item $\mu in {0.0, 0.2, 0.4, 0.6}$.
\end{itemize}

We chose $p + q > 0$ because otherwise no node would be created by the model
after the creation of the initial network. We also avoided large values for
$\mu$ in order to ignore networks with highly-coupled modules.

@@

\begin{itemize}
\item $p1, p2, p3, p4 \in {0.0, 0.2, 0.4, 0.6, 0.8, 1.0}$, with $p1 > 0$ and $p1
  + p2 + p3 + p4 = 1$;
\item $e1, e2, e3, e4 \in {1, 2, 4, 8}$;
\item $\alpha \in {-1, 0, 1, 10, 100, 1000}$;
\item number of modules: $m \in {2, 4, 8, 16, 32}$.
\end{itemize}

@@

\begin{itemize}
  \item $\mu in {0.0, 0.2, 0.4, 0.6}$;
  \item degree exponent distribution: $\gamma \in {2.18, 2.70, 3.35}$;
  \item module size distribution: $\beta \in {0.76, 0.99, 1.58}$;
  \item average degree: $k \in {5, 10, 15, 25}$;
  \item maximum degree: $max_k \in {58, 157, 482}$;
  \item minimum module size: $min_m \in {1, 10, 273}$.
\end{itemize}

In order to choose these values, we analyzed software networks from our sample
with approximately 500 to 2,000 nodes, so no network was much bigger or much
smaller than the synthetic networks. We computed the exponents for the degree
and module size distributions using the maximum likelihood estimation method
CITE-NEWMAN, and then chose the minimum, median and maximum values. For $k$,
$maxk$, and $min_m$, the values extracted from the software networks were
divided by the number of nodes in the network and then multiplied by 1000. We
then selected the minimum, median and maximum values. The parameter $max_m$ was
left unbound to avoid impossible combinations of parameters.

@@

\begin{table}
\caption{Results for the classification of synthetic networks}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | l }
\hline
Model & Networks classified as software-like \\
\hline \\
\hline
BCR+ & 21.18\% \\ % 2012 / 9500
CGW  & 19.40\% \\  % 7524 / 38790
LF   & 31.25\% \\ %  405 / 1296
\hline
\end{tabular}
\label{tab:results}
\end{table}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
Table: Model | Networks classified as software-like
\begin{tabular}{ l | l | l }
\hline
Model & Rule & Accuracy \\
\hline \\
\hline
\multirow{2}{*}{BCR+}
     & $\alpha \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $\alpha < 0.7 \Rightarrow N$ & \\ 
\hline
\multirow{2}{*}{CGW}
     & $p_1 \ge 0.5 \Rightarrow S$ & \multirow{2}{*}{82.3\%} \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\  
\hline
\multirow{2}{*}{LF}   
     & $\gamma \ge 2.44$ & \multirow{2}{*}{78.9\%} \\ 
     & $\gamma \ge 2.44$ &  \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}

>>>>

%   I want less time, so I hire more programmers
%   Thee project can consume more time, due to comunication costs between
% programmers.
%   Unless there is a good division of tasks
%
% (needn't be large)

One of the challenges of software engineering is the reduction of the time
needed to develop or maintain a software system. In

\cite{Brooks1995}

The development and maintenance of large software systems is a big challenge for
software engineering \cite{Northrop2006}. In order to reduce the development
time of such a system, a tempting idea is to assign more developers for the
project.

Because of communication costs between
developers, adding more developers to a project

Adding more developers to a software
project does not

A key to success is the ability to decompose a system into weakly-coupled
modules, so each module can be independently maintained by a distinct team.
Failing to do so results in duplicated code, non-parallelism, one's work
impacting another's work etc.

@@

POR ISSO SURGIRAM software clustering algorithms, also known as software
architecture recovery algorithms \cite{Pollet2007}. In its most common flavor,
these algorithms analyze the dependencies between implementation components,
such as classes, and then group them into modules such as there are few
dependencies between classes in distinct modules.

@@

@@

Of course the success of this approach depends on the similarity between
synthetic networks and networks extracted from real software systems. In this
paper we study three models and show that all of them, by means of a careful
choice of parameter values, are capable of producing software-like networks.

@@

\begin{itemize}
\item $p, q, r \in \{0.0, 0.2, 0.4, 0.6, 0.8, 1.0\}$, with $p + q + r = 1$ and
$p + q > 0$;
\item $din, dout \in \{0, 1, 2, 3, 4\}$;
\item $\mu \in \{0.0, 0.2, 0.4, 0.6\}$.
\end{itemize}

We chose $p + q > 0$ because otherwise no node would be added after the
creation of the initial network. We also avoided large values for $\mu$ in
order to ignore networks with highly-coupled modules.

@@

\begin{itemize}
\item $p1, p2, p3, p4 \in \{0.0, 0.2, 0.4, 0.6, 0.8, 1.0\}$, with $p1 > 0$ and
$p1 + p2 + p3 + p4 = 1$;
\item $e1, e2, e3, e4 \in \{1, 2, 4, 8\}$;
\item $\alpha \in \{-1, 0, 1, 10, 100, 1000\}$;
\item number of modules: $m \in \{2, 4, 8, 16, 32\}$.
\end{itemize}

@@

\begin{itemize}
  \item mixing parameter: $\mu \in \{0.0, 0.2, 0.4, 0.6\}$;
  \item degree exponent distribution: $\gamma \in \{2.18, 2.70, 3.35\}$;
  \item module size distribution: $\beta \in \{0.76, 0.99, 1.58\}$;
  \item average degree: $k \in \{5, 10, 15, 25\}$;
  \item maximum degree: $max_k \in \{58, 157, 482\}$;
  \item minimum module size: $min_m \in \{1, 10, 273\}$.
\end{itemize}

In order to choose these values, we analyzed software networks from our sample
with approximately 500 to 2,000 nodes, so no network was much bigger or much
smaller than the synthetic networks. We computed the exponents for the degree
and module size distributions using the maximum likelihood estimation method
\cite{Clauset2007}, and then chose the minimum, median and maximum values. For
$k$, $maxk$, and $min_m$, the values extracted from the software networks were
divided by the number of nodes in the network and then multiplied by 1000. We
then selected the minimum, median and maximum values. The parameter $max_m$ was
left unbound to avoid impossible combinations of parameters.

@@

\begin{table}
\caption{Results for the classification of synthetic networks}
\centering
\begin{tabular}{|l|l|}
\hline
Model & Networks classified as software-like \\
\hline 
\hline
BCR+ & 21.18\% \\ % 2012 / 9500
\hline
CGW  & 19.40\% \\  % 7524 / 38790
\hline
LF   & 31.25\% \\ %  405 / 1296
\hline
\end{tabular}
\label{tab:results}
\end{table}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
\centering
\begin{tabular}{|l|l|l|}
\hline
Model & Rule & Accuracy \\
\hline 
\hline
\multirow{2}{*}{BCR+}
     & $\alpha \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $\alpha < 0.7 \Rightarrow N$ & \\ 
\hline
\multirow{2}{*}{CGW}
     & $p_1 \ge 0.5 \Rightarrow S$ & \multirow{2}{*}{82.3\%} \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\  
\hline
\multirow{2}{*}{LF}   
     & $\gamma \ge 2.44 \Rightarrow S$ & \multirow{2}{*}{78.9\%} \\ 
     & $\gamma < 2.44 \Rightarrow N$ & \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}
